\section{Architecture Overview}\label{architecture-overview}

This document outlines how video data flows through the kiosk and how
messages are exchanged with the WebSocket server. It also explains where
to tweak common settings.

\subsection{High-Level Flow}\label{high-level-flow}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Video capture} -- \texttt{camera.js} obtains a stream from the
  user's webcam.
\item
  \textbf{Detection} -- frames are processed by
  \texttt{multiFaceDetector.js} and \texttt{handDetector.js} to find
  faces and hands.
\item
  \textbf{Gesture classification} -- detections are fed into
  \texttt{gestureClassifier.js} (head nods/shakes) and
  \texttt{handGestureClassifier.js} (thumb gestures).
\item
  \textbf{Vote dispatch} -- classified gestures trigger
  \texttt{chatClient.js} to send \texttt{vote} messages over WebSocket
  to \texttt{server/wsServer.js}.
\item
  \textbf{Tally display} -- the server broadcasts updates that
  \texttt{voteTally.js} renders in real time.
\end{enumerate}

\subsection{WebSocket Message Formats}\label{websocket-message-formats}

All messages are JSON objects with a \texttt{type} field.

\subsubsection{\texorpdfstring{\texttt{vote}}{vote}}\label{vote}

Sent by clients when a gesture is recognised.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{} \DataTypeTok{"type"}\FunctionTok{:} \StringTok{"vote"}\FunctionTok{,} \DataTypeTok{"gesture"}\FunctionTok{:} \StringTok{"yes"} \ErrorTok{|} \StringTok{"no"} \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

The server increments the tally and broadcasts:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{} \DataTypeTok{"type"}\FunctionTok{:} \StringTok{"vote"}\FunctionTok{,} \DataTypeTok{"delta"}\FunctionTok{:} \FunctionTok{\{} \DataTypeTok{"yes"}\FunctionTok{:} \DecValTok{1} \FunctionTok{\}} \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

(or \texttt{"no"} accordingly)

\subsubsection{\texorpdfstring{\texttt{chat}}{chat}}\label{chat}

Arbitrary chat messages can be sent using:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{} \DataTypeTok{"type"}\FunctionTok{:} \StringTok{"chat"}\FunctionTok{,} \DataTypeTok{"msg"}\FunctionTok{:} \StringTok{"Hello"} \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

The server appends the text to its history and echoes the same object to
all clients.

\subsubsection{\texorpdfstring{\texttt{snapshot}}{snapshot}}\label{snapshot}

When a client connects it receives the current state:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{} \DataTypeTok{"type"}\FunctionTok{:} \StringTok{"snapshot"}\FunctionTok{,} \DataTypeTok{"tally"}\FunctionTok{:} \FunctionTok{\{} \DataTypeTok{"yes"}\FunctionTok{:} \DecValTok{0}\FunctionTok{,} \DataTypeTok{"no"}\FunctionTok{:} \DecValTok{0} \FunctionTok{\},} \DataTypeTok{"chatHistory"}\FunctionTok{:} \OtherTok{[]} \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

\subsection{Customisation}\label{customisation}

\subsubsection{Editing the Question
List}\label{editing-the-question-list}

Questions are loaded from
\href{../public/questions.json}{\texttt{public/questions.json}}. Edit
this JSON file to change what appears in the kiosk.

\subsubsection{Adjusting Gesture
Thresholds}\label{adjusting-gesture-thresholds}

The gesture classifier accepts threshold options.
\href{../src/modules/mbp2020Defaults.js}{\texttt{src/modules/mbp2020Defaults.js}}
provides a preset used in \href{../src/main.js}{\texttt{src/main.js}}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{faceClassifier }\OperatorTok{=} \FunctionTok{createClassifierMap}\NormalTok{(\{}
    \DataTypeTok{deepDebug}\OperatorTok{:}\NormalTok{ DEEP\_DEBUG}\OperatorTok{,}
    \OperatorTok{...}\NormalTok{mbp2020Defaults}\OperatorTok{,}
    \DataTypeTok{pitchThresh}\OperatorTok{:} \FloatTok{0.18}\OperatorTok{,}    \CommentTok{// gentler nod threshold}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{faceClassifier}\OperatorTok{.}\AttributeTok{config}\OperatorTok{.}\AttributeTok{swingMinMs} \OperatorTok{=} \DecValTok{250}\OperatorTok{;}  \CommentTok{// allow slower nods}
\end{Highlighting}
\end{Shaded}

Tweaking values in \texttt{mbp2020Defaults.js}---such as
\texttt{yawThresh} or \texttt{pitchThresh}---alters how sensitive nod
and shake detection is.
