\section{SecureMatch Kiosk}\label{securematch-kiosk}

SecureMatch Kiosk is an interactive web-based application designed for
public engagement through quizzes, gesture-based voting, and real-time
feedback. It uses face detection, gesture classification, and WebSocket
communication to create an engaging experience.

\subsection{Features}\label{features}

\begin{itemize}
\tightlist
\item
  \textbf{Face Detection}: Detects multiple faces using MediaPipe's Face
  Landmarker. See
  \href{src/modules/multiFaceDetector.js}{\texttt{src/modules/multiFaceDetector.js}}.
\item
  \textbf{Gesture Classification}: Recognises vertical nods (``yes''),
  horizontal shakes (``no''), and thumb gestures. The classifier adapts
  to each user's neutral pose and accepts a nod whether you go
  down-then-up or up-then-down. See
  \href{src/modules/gestureClassifier.js}{\texttt{src/modules/gestureClassifier.js}}.
\item
  \textbf{Real-Time Voting}: Displays live vote tallies using Chart.js.
  See
  \href{src/modules/voteTally.js}{\texttt{src/modules/voteTally.js}}.
\item
  \textbf{Visual Feedback}: Faces briefly flash green for ``yes'' and
  red for ``no'' using
  \href{src/modules/overlayRenderer.js}{\texttt{src/modules/overlayRenderer.js}}.
\item
  \textbf{Question Rotation}: Cycles through questions with a countdown
  timer. See
  \href{src/modules/questionRotator.js}{\texttt{src/modules/questionRotator.js}}.
\item
  \textbf{WebSocket Communication}: Synchronizes votes and chat messages
  across clients. See
  \href{src/modules/chatClient.js}{\texttt{src/modules/chatClient.js}}
  and \href{server/wsServer.js}{\texttt{server/wsServer.js}}.
\item
  \textbf{Robust Reconnects}: The client automatically reconnects with
  exponential backoff if the WebSocket drops.
\item
  \textbf{Confetti Animation}: Celebratory confetti animation. See
  \href{src/modules/confettiRenderer.js}{\texttt{src/modules/confettiRenderer.js}}.
\item
  \textbf{QR Code Generation}: Displays QR codes for further discussion
  links. See
  \href{src/modules/qrGenerator.js}{\texttt{src/modules/qrGenerator.js}}.
\item
  \textbf{Reset Button}: Clears the in-memory tallies and face state for
  a new session.
\item
  \textbf{Calibrate Button}: Lets users set the neutral pose for
  reliable detection.
\item
  \textbf{Scoreboard}: Shows current counts for Yes and No votes.
\item
  \textbf{Connection Status}: Shows whether the kiosk is connected to
  the vote server.
\end{itemize}

\subsection{Project Structure}\label{project-structure}

\subsubsection{Key Modules}\label{key-modules}

\begin{itemize}
\tightlist
\item
  \textbf{\href{src/main.js}{\texttt{src/main.js}}}: Entry point for the
  application. Initializes components and starts the main loop.
\item
  \textbf{\href{src/modules/multiFaceDetector.js}{\texttt{src/modules/multiFaceDetector.js}}}:
  Handles face detection using MediaPipe.
\item
  \textbf{\href{src/modules/gestureClassifier.js}{\texttt{src/modules/gestureClassifier.js}}}:
  Classifies gestures based on face landmarks.
\item
  \textbf{\href{src/modules/voteTally.js}{\texttt{src/modules/voteTally.js}}}:
  Manages the vote tally chart.
\item
  \textbf{\href{src/modules/questionRotator.js}{\texttt{src/modules/questionRotator.js}}}:
  Rotates questions and manages the countdown timer.
\item
  \textbf{\href{src/modules/chatClient.js}{\texttt{src/modules/chatClient.js}}}:
  Handles WebSocket communication for votes and chat.
\item
  \textbf{\href{src/modules/confettiRenderer.js}{\texttt{src/modules/confettiRenderer.js}}}:
  Displays confetti animations.
\item
  \textbf{\href{src/store.js}{\texttt{src/store.js}}}: Global state
  management.
\end{itemize}

For a high-level overview of the data flow and WebSocket messages, see
\url{docs/architecture.md}.

\subsection{Setup and Installation}\label{setup-and-installation}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Clone the repository:
  \texttt{sh\ \ \ \ \ git\ clone\ \textless{}repository-url\textgreater{}\ \ \ \ \ cd\ securematch-kiosk}
\item
  Install dependencies (as defined in
  \href{package.json}{\texttt{package.json}}):
  \texttt{sh\ \ \ \ \ npm\ install}
\item
  Start the development server (uses
  \href{vite.config.js}{\texttt{vite.config.js}}):
  \texttt{sh\ \ \ \ \ npm\ run\ dev}
\item
  Start the WebSocket server (defined in \texttt{scripts} in
  \href{package.json}{\texttt{package.json}}, runs
  \href{server/wsServer.js}{\texttt{server/wsServer.js}}):
  \texttt{sh\ \ \ \ \ npm\ run\ start:ws}
\item
  (Optional) Configure the WebSocket URL by creating a \texttt{.env}
  file and setting \texttt{VITE\_WS\_URL}:
  \texttt{VITE\_WS\_URL=ws://localhost:4000}
\item
  Open the application in your browser at \url{http://localhost:5173}
  (port configured in \href{vite.config.js}{\texttt{vite.config.js}}).
\end{enumerate}

\subsection{Starting the Kiosk}\label{starting-the-kiosk}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  In one terminal, start the WebSocket server:
  \texttt{sh\ \ \ \ \ npm\ run\ start:ws}
\item
  In a second terminal, launch the app:
  \texttt{sh\ \ \ \ \ npm\ run\ dev}
\item
  Visit \url{http://localhost:5173} and step into the frame to begin.
\end{enumerate}

\subsection{Usage}\label{usage}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Step into the frame}: The attractor screen (defined in
  \href{index.html}{\texttt{index.html}} and managed by
  \href{src/modules/attractor.js}{\texttt{src/modules/attractor.js}})
  will disappear once a face is detected by
  \href{src/modules/camera.js}{\texttt{src/modules/camera.js}} and
  \href{src/modules/multiFaceDetector.js}{\texttt{src/modules/multiFaceDetector.js}}.
\item
  \textbf{Answer questions}: Questions are displayed from
  \href{src/modules/questionRotator.js}{\texttt{src/modules/questionRotator.js}}.
  Use gestures to vote:

  \begin{itemize}
  \tightlist
  \item
    Nod \textbf{vertically} for ``yes''
  \item
    Shake your head \textbf{horizontally} for ``no''
  \item
    Thumbs up/down are also recognised Gestures are classified by
    \href{src/modules/gestureClassifier.js}{\texttt{src/modules/gestureClassifier.js}}.
    Votes are sent via
    \href{src/modules/chatClient.js}{\texttt{src/modules/chatClient.js}}.
    Faces flash green or red to confirm your choice.
  \end{itemize}
\item
  \textbf{View results}: Live vote tallies are displayed on the chart
  managed by
  \href{src/modules/voteTally.js}{\texttt{src/modules/voteTally.js}}.
\item
  \textbf{Engage further}: Scan the QR code generated by
  \href{src/modules/qrGenerator.js}{\texttt{src/modules/qrGenerator.js}}
  for additional discussion links.
\end{enumerate}

\subsubsection{Custom Questions}\label{custom-questions}

Edit \href{public/questions.json}{\texttt{public/questions.json}} to
change the questions that appear in the kiosk.

\subsection{Dependencies}\label{dependencies}

\begin{itemize}
\tightlist
\item
  \href{https://www.npmjs.com/package/@mediapipe/tasks-vision}{@mediapipe/tasks-vision}
\item
  \href{https://www.chartjs.org/}{chart.js}
\item
  \href{https://github.com/websockets/ws}{ws}
\item
  \href{https://vitejs.dev/}{vite}
\end{itemize}

(See \href{package.json}{\texttt{package.json}} for full list and
versions)

\subsection{Known Issues}\label{known-issues}

\begin{itemize}
\tightlist
\item
  Missing MediaPipe assets: Ensure the
  \href{public/models/face_landmarker.task}{\texttt{face\_landmarker.task}}
  and
  \href{public/wasm/vision_wasm_internal.js}{\texttt{vision\_wasm\_internal.js}}
  files are correctly placed in the \texttt{public/models} and
  \texttt{public/wasm} directories, respectively. These are loaded by
  \href{src/modules/multiFaceDetector.js}{\texttt{src/modules/multiFaceDetector.js}}.
\end{itemize}

For help diagnosing gesture problems, see \url{docs/troubleshooting.md}.

\subsection{License}\label{license}

This project is licensed under the terms of the \href{LICENSE}{MIT
License}.

\subsection{Acknowledgments}\label{acknowledgments}

\begin{itemize}
\tightlist
\item
  MediaPipe for face detection and gesture classification.
\item
  Chart.js for real-time chart rendering.
\item
  WebSocket for real-time communication.
\end{itemize}
